Mahotas: Open source software for scriptable computer vision

### 2013-05-02 paper.tex
ENH Use mahotas.demos.image_path
This achieves file location independence

\begin{python}
import numpy as np
import mahotas
from mahotas.features import surf
from scipy.cluster import vq
\end{python}

The first step is to load the image and convert to 8~bit numbers. In this
case, the conversion is done using standard numpy methods, namely
\code{astype}:

\begin{python}
f = mahotas.imread('luispedro.jpg', as_grey=True)
f = f.astype(np.uint8)
\end{python}

>>>>

\begin{python}
import numpy as np
import mahotas as mh
from mahotas.features import surf
from scipy.cluster import vq
\end{python}

The first step is to load the image and convert to 8~bit numbers. In this
case, the conversion is done using standard numpy methods, namely
\code{astype}. We use the function \code{mahotas.demos.image\_path} to access a
demonstration image.

\begin{python}
import mahotas.demos
impath = mh.demos.image_path('luispedro.jpg')
f = mh.imread(impath, as_grey=True)
f = f.astype(np.uint8)
\end{python}
